Exoplanet population inference and the abundance \\ of Earth analogs from noisy, incomplete catalogs

### 2014-06-11 document/ms.tex
more comments from tim

In detail, any inference of the exoplanet population depends on the choices
made in the pipeline that creates the catalog.
Our results are based on a catalog that only includes single transiting
systems (\citealt{petigura}) so our conclusions---and theirs---must be
considered with this in mind.
In particular, the exclusion of second planets must suppress the inferred rate
density, especially at long periods and small radii.

@@

\item {\bf False positives}\quad
In our inferences, we assume that all of the candidates in the catalog are
\True\ exoplanets.
The rate of false positives in the \kepler\ catalog has been shown to be low
but not negligible (\citealt{morton, fressin-fp}).
Since some of the objects in the catalog are probably false positives, our
inferences about the occurrence rate density are biased high but without
explicitly including a model of false positives, it's hard to say in detail
what effect this would have on the distributions.
In an extension of this work, we could incorporate the effects of false
positives by switching to a mixture model where each object is modeled as a
mixture of \True\ exoplanet and false positive (\citealt{hogg-line}).

@@

\acknowledgments
We would like to thank Erik Petigura (Berkeley) for freely sharing his data
and code.
It is a pleasure to thank
Ruth Angus (Oxford),
Jo Bovy (IAS),
Eric Ford (PSU), and
Ben Montet (Caltech/CfA)
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), NASA
(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
This research builds on ideas generated at a three-week workshop on ``Modern
Statistical and Computational Methods for Analysis of Kepler Data'' at SAMSI
in 2013 June.
This research made use of the NASA \project{Astrophysics Data System}.

@@

>>>>

In detail, any inference of the exoplanet population depends on the choices
made in the pipeline that creates the catalog.
Our results are based on a catalog that only includes single transiting
systems (\citealt{petigura}) so our conclusions---and theirs---must be
considered with this in mind.
In particular, the exclusion of second (and third, and so on) planets must
suppress the inferred rate density, especially at long periods and small
radii.

@@

\item {\bf False positives}\quad
In our inferences, we assume that all of the candidates in the catalog are
\True\ exoplanets.
The rate of false positives in the \kepler\ catalog has been shown to be low
but not negligible (\citealt{morton, fressin-fp}).
Since some of the objects in the catalog are probably false positives, our
inferences about the occurrence rate density are biased high but without
explicitly including a model of false positives, it's hard to say in detail
what effect this would have on the distributions.
In an extension of this work, we could incorporate the effects of false
positives by switching to a mixture model (see \citealt{hogg-line}, for
example) where each object is modeled as a mixture of \True\ exoplanet and
false positive.
In this mixture model, the false positives would be represented using prior
distributions similar to those used by \citet{morton-fp} or
\citet{fressin-fp}.

@@

\acknowledgments
We would like to thank Erik Petigura (Berkeley) for freely sharing his data
and code.
It is a pleasure to thank
Ruth Angus (Oxford),
Jo Bovy (IAS),
Eric Ford (PSU), and
Ben Montet (Caltech/Harvard)
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), NASA
(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
This research builds on ideas generated at a three-week workshop on ``Modern
Statistical and Computational Methods for Analysis of Kepler Data'' at SAMSI
in 2013 June.
This research made use of the NASA \project{Astrophysics Data System}.

@@

\bibitem[Morton(2012)]{morton-fp}
Morton, T.~D.\ 2012, \apj, 761, 6 (\arxiv{1206.1568})
